---
title: "class15"
author: "Meisha Khan"
date: "2/26/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## read sample genotypes data from ENSEMBLE
```{r}
mxl <- read.csv("373531-SampleGenotypes-Homo_sapiens_Variation_Sample_rs8067378.csv")
head(mxl)
```
we want to look at the second column that contains the genotype information

```{r}
table(mxl$Genotype..forward.strand.)
```

## RNA-Seq result analysis for different genotypes of this SNP

```{r}
expre <- read.table("rs8067378_ENSG00000172057.6.txt")
head(expre)
```

does the expression change for different genotypes? 

```{r}
expre[expre$geno == "G/G", ]$exp

```

```{r}
summary ( expre[expre$geno == "G/G", ]$exp )
```

```{r}
hist( expre[expre$geno == "G/G", ]$exp, breaks = 30 )
```

```{r}
x <- 1:10
x
x[x > 5]
```

```{r}
summary ( expre[expre$geno == "A/G", ]$exp )
```

```{r}
summary ( expre[expre$geno == "A/A", ]$exp )
```

```{r}
mean ( expre[expre$geno == "A/A", ]$exp )
```


```{r}
#genos <- data.frame()
```


## Try a boxplot

we will use the `boxplot()` function and the input data will be **expre**. HOw do we draw a useful plot? 


```{r}
boxplot(exp ~ geno, data = expre, notch = T)
```

How many samples are we looking at here? 

```{r}
nrow(expre)
```


















