---
title: "class17"
author: "Meisha Khan"
date: "3/4/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Coronavirus

Here we analyze infection data for the 2019 novel Coronavirus COVID-19 (2019-nCoV) epidemic. The raw data is pulled from the Johns Hopkins University Center for Systems Science and Engineering (JHU CCSE) Coronavirus repository.

A CSV file is available here https://github.com/RamiKrispin/coronavirus-csv


```{r}
url <- "https://tinyurl.com/COVID-2019"
virus <- read.csv(url)

tail(virus)
```


> Q1. How many total infected cases are there around the world? 

```{r}
total_cases <- (sum(virus$cases))
total_cases
```


> Q2. How many deaths linked to infected cases have there been? 

Let's have a look at the *$type* column

```{r}
table(virus$type)
```

```{r}
death <- (virus$type == "death")
(virus[death,])
```

```{r}
total_death <- (sum(virus[death,"cases"]))
total_death
```

> Q3. What is the overall death rate? US? Italy? China? 


```{r}
round(total_death/total_cases * 100, 2)
```

> Q4. What is the overall China death rate?

```{r}
China <- (virus$Country.Region == "mainland China")
China

```


> Q5. What is the overall Italy death rate?

> Q6. What is the overall Iran death rate?

> Q7. What is the overall in the US death rate?


Submit a link to your Knitted GitHub document (i.e. the .md file)








