---
title: 'Class 6: R Functions'
author: "Meisha Khan"
date: "1/24/2020"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## This is a level 2 heading

This is **regular** old *text*!

### This is a level 3 heading



and a list of stuff

- thing one
- thing two
- and another thing



```{r}
plot(1:5, col="pink", type="o")
```

let's insert a code chunk with the shortcut `Option-CMD-i`:

```{r}
x <- c(1:10)
x
```


here is my analysis of new data. it looks ok.. the mean of your data is `r mean(x)`.

## More on reading input files

We will use the read.table input
must have "file" for read.table
other common arguments: sep = "\t" (tab), header = (TRUE/FALSE)

## TEST FILE 1
```{r}
x <- read.table("test1.txt", header = TRUE, sep = ",")
x
```

OR

```{r}
x <- read.csv("test1.txt")
x
```

## TEST FILE 2

```{r}
x2 <- read.table("test2.txt", header = TRUE, sep = "$")
x2
```

## TEST FILE 3

```{r}
x3 <- read.table("test3.txt")
x3
```




## OUR FIRST FUNCTION

This is an example function named `add` with input `x` and `y`

```{r}
add <- function(x, y=1) {
 # Sum the input x and y
 x + y
}
```

Let's try using it here...

```{r}
add(c(1,6,2), 4)
```

OR

```{r}
add(x=c(1,6,2), y=4)
```
same thing

other examples: 

1. 
```{r}
add(x=1, y=4)
add(1, 4)
add(1)
```

2. 
```{r}
add( c(1, 2, 3) )
add( c(1, 2, 3), 4 )
```

### if you do a function more than 3 times, its time to **function**

Start with a working code snippet, simplify, reduce calculation duplication, and finally *turn it into a function!*

range function calculates min and max

```{r}
x <- c(10,4,22,6)
min(x)
max(x)
range(x)
```

A 2nd example function to re-scale data to lie between 0 and 1

```{r}
rescale <- function(x) {
 rng <-range(x)
 (x - rng[1]) / (rng[2] - rng[1])
}
```

Let's try using it here...

```{r}
rescale(1:10)
```

what happens if NA is used? 

```{r}
rescale( c(1:10, NA))
```
we broke it - wmhy? well...

```{r}
x <- c(1:10, na.rm = FALSE)
 rng <-range(x)
 rng
```
here we ommitted NA from being included

```{r}
x <- c(1:10, na.rm = TRUE)
 rng <-range(x)
 rng
```

FIX FOR missing values NAs

```{r}
rescale2 <- function(x) {
 rng <-range(x, na.rm=TRUE)
 (x - rng[1]) / (rng[2] - rng[1])
}
```

```{r}
rescale2( c(1:10, NA))
```

take piece of code, extract code, make it simpler, probably break it, figure whats broken, reiterate it, and then finally find function

```{r}
rescale3 <- function(x, na.rm=TRUE, plot=FALSE) {
  
 rng <-range(x, na.rm=na.rm)
 print("Hello")
 
 answer <- (x - rng[1]) / (rng[2] - rng[1])
 
 print("is it me you are looking for?")
 
 if(plot) {
   print("please don't sing to me")
 plot(answer, typ="b", lwd=4)
 }
 
 print("I can see it in ...")
 return(answer)
 
}
```

```{r}
rescale3(x, plot=TRUE)
```


