---
title: 'Class 6: R Functions'
author: "Meisha Khan"
date: "1/24/2020"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## This is a level 2 heading

This is **regular** old *text*!

### This is a level 3 heading



and a list of stuff

- thing one
- thing two
- and another thing



```{r}
plot(1:5, col="pink", type="o")
```

let's insert a code chunk with the shortcut `Option-CMD-i`:

```{r}
x <- c(1:10)
x
```


here is my analysis of new data. it looks ok.. the mean of your data is `r mean(x)`.

## More on reading input files

We will use the read.table input
must have "file" for read.table
other common arguments: sep = "\t" (tab), header = (TRUE/FALSE)

## TEST FILE 1
```{r}
x <- read.table("test1.txt", header = TRUE, sep = ",")
x
```

OR

```{r}
x <- read.csv("test1.txt")
x
```

## TEST FILE 2

```{r}
x2 <- read.table("test2.txt", header = TRUE, sep = "$")
x2
```

## TEST FILE 3

```{r}
x3 <- read.table("test3.txt")
x3
```




## OUR FIRST FUNCTION

This is an example function named `add` with input `x` and `y`

```{r}
add <- function(x, y=1) {
 # Sum the input x and y
 x + y
}
```

Let's try using it here...

```{r}
add(c(1,6,2), 4)
```

OR

```{r}
add(x=c(1,6,2), y=4)
```
same thing

what about? 
```{r eval = FALSE}
add(1,6,2)
```
doesnt work 

```{r eval= FALSE}
add(1, 2, 2)
add(x=1, y=“b”)
```

other examples: 

1. 
```{r}
add(x=1, y=4)
add(1, 4)
add(1)
```

2. 
```{r}
add( c(1, 2, 3) )
add( c(1, 2, 3), 4 )
```

### if you do a function more than 3 times, its time to **function**

Start with a working code snippet, simplify, reduce calculation duplication, and finally *turn it into a function!*

range function calculates min and max

```{r}
x <- c(10,4,22,6)
min(x)
max(x)
range(x)
```

A 2nd example function to re-scale data to lie between 0 and 1

```{r}
rescale <- function(x) {
 rng <-range(x)
 (x - rng[1]) / (rng[2] - rng[1])
}
```

Let's try using it here...

```{r}
rescale(1:10)
```

what happens if NA is used? 

```{r}
rescale( c(1:10, NA))
```
we broke it - wmhy? well...

```{r}
x <- c(1:10, na.rm = FALSE)
 rng <-range(x)
 rng
```
here we ommitted NA from being included

```{r}
x <- c(1:10, na.rm = TRUE)
 rng <-range(x)
 rng
```

FIX FOR missing values NAs

```{r}
rescale2 <- function(x) {
 rng <-range(x, na.rm=TRUE)
 (x - rng[1]) / (rng[2] - rng[1])
}
```

```{r}
rescale2( c(1:10, NA))
```

take piece of code, extract code, make it simpler, probably break it, figure whats broken, reiterate it, and then finally find function

```{r}
rescale3 <- function(x, na.rm=TRUE, plot=FALSE) {
  
 rng <-range(x, na.rm=na.rm)
 print("Hello")
 
 answer <- (x - rng[1]) / (rng[2] - rng[1])
 
 print("is it me you are looking for?")
 
 if(plot) {
   print("please don't sing to me")
 plot(answer, typ="b", lwd=4)
 }
 
 print("I can see it in ...")
 return(answer)
 
}
```

```{r}
rescale3(x, plot=TRUE)
```




## SECTION 1B

To use the functions from any package we have installed, we use `library` function to load it

```{r}
library(bio3d)
```


# Can you improve this analysis code?

```{r}
s1 <- read.pdb("4AKE") # kinase with drug
s2 <- read.pdb("1AKE") # kinase no drug
s3 <- read.pdb("1E4Y") # kinase with drug

s1.chainA <- trim.pdb(s1, chain="A", elety="CA")
s2.chainA <- trim.pdb(s2, chain="A", elety="CA")
s3.chainA <- trim.pdb(s1, chain="A", elety="CA")

s1.b <- s1.chainA$atom$b
s2.b <- s2.chainA$atom$b
s3.b <- s3.chainA$atom$b

plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor")
plotb3(s2.b, sse=s2.chainA, typ="l", ylab="Bfactor")
plotb3(s3.b, sse=s3.chainA, typ="l", ylab="Bfactor")
```



```{r}
hc <- hclust( dist( rbind(s1.b, s2.b, s3.b) ) )
plot(hc)
```

**Q1. What type of object is returned from the read.pdb() function?** 
- (same deal as read.delim/read.csv, etc)
- returns a list of class 'pdb" with several components

```{r}
s1 <- read.pdb("4AKE")
s1
```


```{r}
class(s1)
```
sse = secondary structure element 

```{r}
str(s1)
```


```{r}
s1$seqres
```

```{r}
aa321(s1$seqres)
```

**Q2. What does the trim.pdb() function do?**

- trim a PBD object to a subset of atoms
- produce a new smaller pdb object, containing a subset of atoms, from a given larger pdb object.

```{r}
s1.chainA <- trim.pdb(s1, chain="A", elety="CA")
s1.chainA
```

```{r}
class(s1.chainA)
```

```{r}
str(s1.chainA)
```


**Q3. What input parameter would turn off the marginal black and grey rectangles in the plots and what do they represent in this case?**

### make simplified code omg 

```{r}
plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor")
points(s2.b, col= "blue", typ = "l")
points(s3.b, col= "red", typ= "l")
```


#fixing code

s1 <- read.pdb("4AKE") # kinase with drug
s2 <- read.pdb("1AKE") # kinase no drug
s3 <- read.pdb("1E4Y") # kinase with drug
s1.chainA <- trim.pdb(s1, chain="A", elety="CA")
s2.chainA <- trim.pdb(s2, chain="A", elety="CA")
s3.chainA <- trim.pdb(s3, chain="A", elety="CA")
s1.b <- s1.chainA$atom$b
s2.b <- s2.chainA$atom$b
s3.b <- s3.chainA$atom$b
plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor")
plotb3(s2.b, sse=s2.chainA, typ="l", ylab="Bfactor")
plotb3(s3.b, sse=s3.chainA, typ="l", ylab="Bfactor")


boil down to essential snippet: 
- read.pdb 
- trim.pdb
- plotb3
--> generalize, input for plot 

put it into body of function and see what happens 


s1 <- read.pdb("4AKE") # kinase with drug
s2 <- read.pdb("1AKE") # kinase no drug
s3 <- read.pdb("1E4Y") # kinase with drug

```{r}
s <- function(x) 
s.pbd <- read.pdb(x)
s("4AKE")
```

```{r}
s <- function(protein) {
read.pdb(protein)
}
s("4AKE")
```

```{r}
s1 <- read.pdb("4AKE") # kinase with drug
s2 <- read.pdb("1AKE") # kinase no drug
s3 <- read.pdb("1E4Y") # kinase with drug
```

```{r}
s <- read.pdb(protein)
s("4AKE")
```


```{r}
s <- function(protein) {
read.pdb(protein)
}
a <-s("4AKE")
```
```{r}
a
```


s1.chainA <- trim.pdb(s1, chain="A", elety="CA")
s2.chainA <- trim.pdb(s2, chain="A", elety="CA")
s3.chainA <- trim.pdb(s3, chain="A", elety="CA")

schain <- function(sA, chain="A", elety="CA")
trim.pdb(sA)
schain(sA)

```{r}
a.schain <- trim.pdb(a, chain="A", elety="CA" )
a.schain
```


s1.b <- s1.chainA$atom$b
s2.b <- s2.chainA$atom$b
s3.b <- s3.chainA$atom$b
 
atoms <- a.schain$atom$b

```{r}
atoms <- a.schain$atom$b
atoms
```
 
```{r}
s1.b <- s1.chainA$atom$b
s2.b <- s2.chainA$atom$b
s3.b <- s3.chainA$atom$b
s1.b
```
 
 
plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor")
plotb3(s2.b, sse=s2.chainA, typ="l", ylab="Bfactor")
plotb3(s3.b, sse=s3.chainA, typ="l", ylab="Bfactor")
 
 
plot.proteins <- (atoms, sse=s1.chainA, typ="l", ylab="Bfactor")
plot_colors <- (col = "pink", "blue", "purple")

```{r}
plot.proteins <- (atoms, sse=s1.chainA, typ="l", ylab="Bfactor")
plot_colors <- (col = "pink", "blue", "purple")
```


combine all into one function 

s <- function(protein) {
read.pdb(protein)
}
s("4AKE")
 
a.schain <- trim.pdb(a, chain="A", elety="CA" )
a.schain

atoms <- a.schain$atom$b
atoms

plot.proteins <- (atoms, sse=s1.chainA, typ="l", ylab="Bfactor")
plot_colors <- (col = "pink", "blue", "purple")


s1 <- read.pdb("4AKE") # kinase with drug
s2 <- read.pdb("1AKE") # kinase no drug
s3 <- read.pdb("1E4Y") # kinase with drug

protein_analysis_plots <- function(protein) {
s <- read.pdb(protein)
s.chain <- trim.pdb(s, chain="A", elety="CA")
atoms <- (s.chain$atom$b)
plot.proteins <- (atoms, sse=s1.chainA, typ="l", ylab="Bfactor", col= plot_colors[i])
plot_colors <- c("pink", "blue", "purple")
protein <- c(4AKE", "1AKE", "1E4Y")
protein_analysis_plots(protein)
}

```{r}
protein_analysis_plots <- function(protein) {
s <- read.pdb(protein)
s.chain <- trim.pdb(s, chain="A", elety="CA")
atoms <- (s.chain$atom$b)
plot.proteins <- (atoms, sse=s1.chainA, typ="l", ylab="Bfactor", col= plot_colors[i])
plot_colors <- c("pink", "blue", "purple")
protein <- c(4AKE", "1AKE", "1E4Y")
protein_analysis_plots(protein)
}

```

```{r}
function
```

  for (i in 1:length(protein[i]))
    plot(protein_analysis_plot)
