---
title: 'class06 homework: writing functions'
author: "Meisha Khan"
date: "1/31/2020"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
library(bio3d)
```


# Can you improve this code? 

```{r}
s1 <- read.pdb("4AKE") # kinase with drug
s2 <- read.pdb("1AKE") # kinase no drug
s3 <- read.pdb("1E4Y") # kinase with drug
s1.chainA <- trim.pdb(s1, chain="A", elety="CA")
s2.chainA <- trim.pdb(s2, chain="A", elety="CA")
s3.chainA <- trim.pdb(s1, chain="A", elety="CA")
s1.b <- s1.chainA$atom$b
s2.b <- s2.chainA$atom$b
s3.b <- s3.chainA$atom$b
plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor")
plotb3(s2.b, sse=s2.chainA, typ="l", ylab="Bfactor")
plotb3(s3.b, sse=s3.chainA, typ="l", ylab="Bfactor")
```

## overall goal of this code: *Create a small pdb object from large pdb files and isolate a subset of atoms 

Inputs of this code include: 
- .pdb objects read via read.pdb() function and trimmed via trim.pdb() function
- atom selections obtained after trimming are inputed into graphs

Output of this code include: 
- Collective ine graph of analyzed proteins

# main functions: 
```{r}
s1 <- read.pdb("4AKE")
s1.chainA <- trim.pdb(s1, chain="A", elety="CA")
s1.b <- s1.chainA$atom$b
plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor")
```


# simplify

file : s1 <- read.pdb(s1)
trim: s1.chainA <- trim.pdb(s1, chain="A", elety="CA")
chain: s1.b <- s1.chainA$atom$b
plot: plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor")

#need to loop file for iterations to appear on one graph 
for (i in 1:length(protein[i]))
plot(protein_analysis_plot)
#code did not iterate inputs, could not figure it out :(

protein_analysis_plot <- function(file, trim, chain, plot) {
s1 <- read.pdb(file)
s1.chainA <- trim.pdb(s1, chain="A", elety="CA")
s1.b <- s1.chainA$atom$b
plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor")
}

```{r}
protein_analysis_plot <- function(s1) {
    s1.chainA <- trim.pdb(s1, chain="A", elety="CA")
    s1.b <- s1.chainA$atom$b
  plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor", col = rainbow(3))

}
s1 <- read.pdb("4AKE")
protein_analysis_plot(s1)
```









