---
title: 'Class10: Machine Learning Project'
author: "Meisha Khan"
date: "2/7/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Get our input data

Our data for today comes from the Wisconsin Breast Cancer Diagnostic Data Set 

```{r}
wisc.df <- read.csv("WisconsinCancer.csv")
wisc.df
head(wisc.df)
```

```{r}
wisc.data <- as.matrix(wisc.df[,3:32])
head(wisc.data)
```


> Q. How many patients are there in this dataset? 

```{r}
nrow(wisc.data)
```

> Q. How many cancer (malignant) and non-cancer (benign) patients are there? 

```{r}
wisc.df$diagnosis
```

```{r}
table(wisc.df$diagnosis)
```

```{r}
sum(wisc.df$diagnosis == "M")
```


> Q. How many column names contain the "mean" of the data? 

#grep - patterns in a vector (mean in column names, will tell you where they are)

```{r}
colnames(wisc.df)
```

# value = TRUE gives you matches
```{r}
grep(("_mean"), colnames(wisc.df), ignore.case = TRUE, value = TRUE)
```

# value = FALSE gives you how many matchers there are
```{r}
grep(("_mean"), colnames(wisc.df), ignore.case = TRUE)
```

# sum of mean matches

```{r}
length(grep("_mean", colnames(wisc.df)))
```

## Enter Principal Component Analysis

First we need to check whether our input data should be scaled 
- look at mean and st dev of each column
- if different, need to scale 

lets check the sd() and means()  of all our columns in `wisc.data`

apply(x, 2, SD) --> (x, column or row, function)
1 = row
2 = column 

round --> number at end corresponds to sigfigs
```{r}
round(apply(wisc.data, 2, sd), 2)
```

```{r}
# Perform PCA on wisc.data by completing the following code
wisc.pr <- prcomp( wisc.data, scale=TRUE )
summary(wisc.pr)
```

```{r}
biplot(wisc.pr)
```

This is a hot mess! We need to cook our own PCA plot. To do this we need to access the results within the `wisc.pr` object.

```{r}
attributes(wisc.pr)
```

We want the $x component to make our PCA plot!
```{r}
plot(wisc.pr$x[,1], wisc.pr$x[,2], col=wisc.df$diagnosis)
```



Wow, this looks cool! There is a separation of the red (cancer) from black (non-cancer) samples.

### Hierarchical clustering

Can we find a separation of cancer from non-cancer using a clustering method on the original input data?

For this we will use the `hclust()` function on the `wisc.data` object that we used for PCA.

```{r}
hc <- hclust( dist(wisc.data) )
plot(hc)
```

I don't know where it is good to *cut* a tree like this...

I can cluster in PC space - in other words use the results of PCA to do my clustering

```{r}
wisc.pr.hc <- hclust( dist(wisc.pr$x[,1:3]), method="ward.D2" )
plot(wisc.pr.hc)
```

```{r}
grps <- cutree(wisc.pr.hc, k=2)
table(grps)
```

```{r}
table(grps, wisc.df$diagnosis)
```

```{r}
plot(wisc.pr$x[,1], wisc.pr$x[,2], col=grps)
```


## Prediction using our PCA model 

We will use the predict() function that will take our PCA model from before and new cancer cell data and project that data onto our PCA space.

#url <- "new_samples.csv"

```{r}
url <- "https://tinyurl.com/new-samples-CSV"
new <- read.csv(url)
npc <- predict(wisc.pr, newdata=new)
npc
```


```{r}
plot(wisc.pr$x[,1:2], col=wisc.df$diagnosis)
points(npc[,1], npc[,2], col="blue", pch=16, cex=3)
text(npc[,1], npc[,2], labels=c(1,2), col="white")
```




building capability in R for any numeric set of data (cancer, eating, etc)




















